---
title: "Data_cleaning"
format: html
self-contained : true
editor: visual
---

```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(readr)
library(rstatix)
library(janitor)
library(dplyr)
library(knitr)
library(haven)
library(gt)
library(gtsummary)
library(survey)
```

###Load data

```{r}
NHANES_Demo_1718 <- read_xpt("Data/DEMO_J.xpt")
NHANES_Demo_1516 <- read_xpt("Data/DEMO_I.xpt")
NHANES_Demo_1314 <- read_xpt("Data/DEMO_H.xpt")
```

```{r}
NHANES_BMI_1718 <- read_xpt("Data/BMX_J.xpt")
NHANES_BMI_1516 <- read_xpt("Data/BMX_I.xpt")
NHANES_BMI_1314 <- read_xpt("Data/BMX_H.xpt")
```

###DM(Diabetes Melliitus)

```{r}
NHANES_DM_1718 <- read_xpt("Data/DIQ_J.xpt")
NHANES_DM_1516 <- read_xpt("Data/DIQ_I.xpt")
NHANES_DM_1314 <- read_xpt("Data/DIQ_H.xpt")
```

## HINSUR

```{r}
NHANES_Hinsur_1718 <- read_xpt("Data/HIQ_J.xpt")
NHANES_Hinsur_1516 <- read_xpt("Data/HIQ_I.xpt")
NHANES_Hinsur_1314 <- read_xpt("Data/HIQ_H.xpt")
```

## (Medcon)

```{R}
NHANES_MC_1718 <- read_xpt("Data/MCQ_J.xpt")
NHANES_MC_1516 <- read_xpt("Data/MCQ_I.xpt")
NHANES_MC_1314 <- read_xpt("Data/MCQ_H.xpt")
```

## Physical Activty

```{r}
NHANES_PA_1718 <- read_xpt("Data/PAQ_J.xpt")
NHANES_PA_1516 <- read_xpt("Data/PAQ_I.xpt")
NHANES_PA_1314 <- read_xpt("Data/PAQ_H.xpt")
```

#Smoking

```{R}
NHANES_SMK_1718 <- read_xpt("Data/SMQ_J.xpt")
NHANES_SMK_1516 <- read_xpt("Data/SMQ_I.xpt")
NHANES_SMK_1314 <- read_xpt("Data/SMQ_H.xpt")
```

```{R}
NHANES_demo_merged <- bind_rows(NHANES_Demo_1314, 
                         NHANES_Demo_1516, 
                         NHANES_Demo_1718)
```

```{r}
NHANES_BMI_merged <- bind_rows(NHANES_BMI_1314, 
                         NHANES_BMI_1516, 
                         NHANES_BMI_1718)
```

```{r}
NHANES_DM_merged <- bind_rows(NHANES_DM_1314, 
                         NHANES_DM_1516, 
                         NHANES_DM_1718)
```

```{r}
NHANES_Hinsur_merged <- bind_rows(NHANES_Hinsur_1314, 
                         NHANES_Hinsur_1516, 
                         NHANES_Hinsur_1718)
```

```{R}
NHANES_MC_merged <- bind_rows(NHANES_MC_1314, 
                         NHANES_MC_1516, 
                         NHANES_MC_1718)
```

```{r}
NHANES_PA_merged <- bind_rows(NHANES_PA_1314, 
                         NHANES_PA_1516, 
                         NHANES_PA_1718)
```

```{r}
NHANES_SMK_merged <- bind_rows(NHANES_SMK_1314, 
                         NHANES_SMK_1516, 
                         NHANES_SMK_1718)
```

## Create analytic sample

```{R}
BMI_vars <- NHANES_BMI_merged %>% select( SEQN, BMXBMI)
SMK_vars <- NHANES_SMK_merged %>% select(SEQN, SMQ020, SMQ621)
DM_vars <- NHANES_DM_merged %>% select(SEQN, DIQ010)
Hinsur_vars <- NHANES_Hinsur_merged %>% select(SEQN , HIQ011)
MC_vars <- NHANES_MC_merged %>% select(SEQN, MCQ160A, MCQ195)
PA_vars <- NHANES_PA_merged %>% select(SEQN, PAQ605, PAQ610, PAQ620, PAD615, PAQ625, PAD630)
```

#MET Score coding

```{r}
PA_vars <- PA_vars %>%
  mutate(Days_vig = case_when(
    PAQ610 == 77 ~ NA_real_,
    PAQ610 == 99 ~ NA_real_,
    TRUE ~ as.numeric(PAQ610)
  ),
  mins_vig = case_when(
    PAD615 == 7777 ~ NA_real_,
    PAD615 == 9999 ~ NA_real_,
    TRUE ~ as.numeric(PAD615)
  ),
  days_mod = case_when(
    PAQ625 == 77 ~ NA_real_,
    PAQ625 == 99 ~ NA_real_,
    TRUE ~ as.numeric(PAQ625)
  ),
  mins_mod = case_when(
    PAD630 == 7777 ~ NA_real_,
    PAD630 == 9999 ~ NA_real_,
    TRUE ~ as.numeric(PAD630)
  )
  )
```

```{R}
PA_vars$MET_vig <- (PA_vars$mins_vig*8)*PA_vars$Days_vig

PA_vars$MET_mod <- (PA_vars$mins_mod*4)*PA_vars$days_mod
PA_vars$MET_total <- PA_vars$MET_vig + PA_vars$MET_mod
```

```{r}
NHANES_analytic <- NHANES_demo_merged %>%
  left_join(BMI_vars,   by = "SEQN") %>%
  left_join(SMK_vars,   by = "SEQN") %>%
  left_join(DM_vars,    by = "SEQN") %>%
  left_join(Hinsur_vars, by = "SEQN") %>%
  left_join(MC_vars,    by = "SEQN") %>%
  left_join(PA_vars,    by = "SEQN")

```

#BMI catagorical

Underweight/Normal = 0 Overweight = 1 Obese = 2

```{R}
NHANES_analytic <- NHANES_analytic %>%
  mutate(BMI_cat = case_when(
    BMXBMI < 25 ~ "Underweight/Normal",
    BMXBMI >= 25 & BMXBMI <= 30 ~ "Overweight",
    BMXBMI > 30 ~ "Obese",
    TRUE ~ NA_character_
  ))
```

#Mutate / Recode

Arthritis: MCQ 160a : 1 = Yes, 2= No , Other = 0

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    Arthritis = case_when(
      MCQ160A == 1 ~ 1,
      MCQ160A == 2 ~ 0,
      MCQ160A == 9 ~ 0,
      TRUE ~ NA_real_
    ),
    Osteoarthritis = if_else(MCQ195 == 1, "Yes", "No", missing = NA),
    age_cat = case_when(
      RIDAGEYR >= 20 & RIDAGEYR <= 29 ~ "20-29",
      RIDAGEYR >= 30 & RIDAGEYR <= 44 ~ "30-44",
      RIDAGEYR >= 45 & RIDAGEYR <= 64 ~ "45-64",
      RIDAGEYR >= 65 ~ "65+"
    ),
    Hinsur_yn = case_when(
      HIQ011 == 1 ~ "Yes",
      HIQ011 == 2 ~ "No",
      TRUE ~ NA_character_
    ),
    smk_status = case_when(
      SMQ020 == 1 ~ "Yes",
      SMQ020 == 2 ~ "No"
    ),
     RE_cat = case_when(
       RIDRETH3 == 1 ~ "Mexican American",
       RIDRETH3 == 3 ~ "White",
       RIDRETH3 == 4 ~ "Black",
       RIDRETH3 == 6 ~ "Asian",
       RIDRETH3 == 2 |
       RIDRETH3 == 7 ~ "Mixed/Other"
     ),
    Sex_cat = case_when(
      RIAGENDR == 1 ~ "Male",
      RIAGENDR == 2 ~ "Female"
    ),
    Edu_yn = case_when(
      DMDEDUC2 == 5 ~ "College graduate and above",
      DMDEDUC2 == 1 ~ "Less than college education",
      DMDEDUC2 == 2 ~ "Less than college education",
      DMDEDUC2 == 3 ~ "Less than college education",
      DMDEDUC2 == 4 ~ "Less than college education",
      DMDEDUC2 == 7 ~ NA_character_,
      DMDEDUC2 == 9 ~ NA_character_,
      TRUE ~ NA_character_
    ),
    Income = case_when(
      INDFMPIR > 0 & INDFMPIR <= 1.3 ~ "<130% FPL",
      INDFMPIR > 1.3 & INDFMPIR <= 3.5 ~ "130-350% FPL",
      INDFMPIR > 3.5 ~ ">350% FPL"
    ),
    Diabetes = case_when(
      DIQ010 == 1 ~ "Yes",
      DIQ010 == 2 ~ "No",
      DIQ010 == 3 ~ "No",
      DIQ010 == 9 ~ "No",
      TRUE ~ NA_character_
    ),
    MET_tertile = ntile(MET_total, 3),  # splits into 3 equal groups
         MET_tertile = factor(MET_tertile,
                              levels = c(1, 2, 3),
                              labels = c("Low", "Medium", "High")))
```

```{r}
NHANES_analytic <-  NHANES_analytic %>%
  mutate(subpop1 = case_when(
    age_cat == "20-29" | age_cat == "30-44" | age_cat == "45-64" & Arthritis == 1 ~ 1, .default = 0
  ))

NHANES_analytic %>%
  filter(subpop1 == 1) %>%
  nrow()
```

8950 with correct age and has arthritis

# Missing values

```{r}
NHANES_analytic<- NHANES_analytic %>%
  mutate(miss_dv = case_when(
    is.na(Osteoarthritis)  ~ 1,  
    .default = 0))



NHANES_analytic <- NHANES_analytic %>%
  mutate(miss_iv = case_when(
    is.na(MET_total) ~ 1,  
    .default= 0)) 

```

Counts of missing

```{r}
NHANES_analytic %>%
  filter(subpop1 == 1 & miss_dv == 0) %>%
  nrow()

NHANES_analytic %>%
  filter(subpop1 == 1 & miss_iv == 0) %>%
  nrow()
```

#subpop2

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop2 = case_when(
    subpop1 == 1 & miss_dv == 0 &
      miss_iv == 0 ~ 1,
    .default = 0
  ))

NHANES_analytic %>%
  filter(subpop2 == 1) %>%
  nrow()
```

#Svey Design

```{r}

OA_subpop <- NHANES_analytic %>%
  filter(subpop2 == 1)


OAsvyset <- svydesign(id=~SDMVPSU, weights=~WTMEC2YR, strata=~SDMVSTRA, nest=TRUE, data= OA_subpop)

```

```{R}
table(NHANES_analytic$BMI_cat) 
```

#Total: 29400 Participants of 64 variables

```{R}
# of cases age 
NHANES_analytic %>%
  filter(RIDAGEYR >= 20 & RIDAGEYR <= 65) %>%
  nrow()

NHANES_analytic
```

20-65 yo : 13141

#Arthritis type

Osteo = 1 All other = 0

```{R}
NHANES_analytic %>%
  filter(Osteoarthritis == 1) %>%
  nrow()
```

Total yes osteo 2021

```{r}
table(NHANES_analytic$Osteoarthritis)
```

```{r}
NHANES_analytic <- NHANES_analytic %>%
  select(MET_vig, MET_mod, MET_total, Hinsur_yn, RE_cat, Arthritis, Osteoarthritis, BMI_cat, age_cat, smk_status, Sex_cat, Income, Edu_yn, Diabetes, WTMEC2YR, SDMVPSU, SDMVSTRA)
```

```{r}
Analytic_sample <- NHANES_analytic %>% drop_na( BMI_cat)
```

#Missing BMI \<- after: 25816

```{r}
Analytic_sample2 <- Analytic_sample %>%
  drop_na(age_cat)
```

#Drop missing age -\> 16101

```{r}
Age_fil_Sample <- Analytic_sample2 %>%
  filter(age_cat %in% c( "20-29", "30-44", "45-64"))
```

###Select for age -\> 12243

#Filter for NA MET

```{r}
MET_sample <- Age_fil_Sample %>%
  drop_na(MET_total, MET_mod, MET_vig)
```

2277 after MET na

#Filter for Osteo NA

```{r}
Fin_sample <- MET_sample %>%
  drop_na(Osteoarthritis, Hinsur_yn, RE_cat)
```

Fin sample \<- 424 participants.

Drop confounders

```{r}
Fin_sample <- Fin_sample %>% 
  drop_na( Income, Edu_yn, Diabetes)
```

Fin sample = 376

```{r}
library(moonBook)

head(Fin_sample)

table1 <- mytable(Osteoarthritis ~ MET_vig + MET_mod + MET_total + Hinsur_yn + RE_cat + BMI_cat + age_cat + smk_status+ Sex_cat + Income + Edu_yn + Diabetes, data = Fin_sample) 

table1
```

```{r}
options(survey.lonely.psu = "adjust")

OAsvyset %>% 
  tbl_svysummary(
    by = Osteoarthritis,
    include = c(MET_vig, MET_mod, MET_total, Hinsur_yn, RE_cat, BMI_cat, age_cat, smk_status, Osteoarthritis, Sex_cat,  Income, Edu_yn, Diabetes),
    label = list(
      MET_vig    ~ "Vigorous Physical Activity (MET)",
      MET_mod    ~ "Moderate Physical Activity (MET)",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat   ~ "Sex",
      Income ~ "Income",
      Edu_yn ~ "Higher Education",
      Diabetes ~ "Diabetes"
    )
  ) %>%
  bold_labels() %>%
  as_gt()%>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 based on Osteoarthritis")


```

```{r}
# Convert survey design variables to dataframe for tbl_summary
OA_subpop %>%
  select(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile) %>%
  tbl_summary(
    by      = Osteoarthritis,
    missing = "no",
    label = list(
      MET_tertile    ~ "MET score by Tertiles",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 based on Osteoarthritis") %>%
  gtsave(filename = "Table1_byOA.docx")

```

### Table 1 by exposure

```{r}
# Convert survey design variables to dataframe for tbl_summary
OA_subpop %>%
  select(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile) %>%
  tbl_summary(
    by      = MET_tertile,
    missing = "no",
    label = list(
      Osteoarthritis ~ "Has Osteoarthritis?",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 by MET level") %>%
  gtsave(filename = "Table1_OA_byMET.docx")
```
