---
title: "Data_cleaning"
format: html
self-contained : true
editor: visual
---

```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(readr)
library(rstatix)
library(janitor)
library(dplyr)
library(knitr)
library(haven)
library(gt)
library(gtsummary)
library(survey)
```

###Load data

```{r}
NHANES_Demo_1718 <- read_xpt("Data/DEMO_J.xpt")
NHANES_Demo_1516 <- read_xpt("Data/DEMO_I.xpt")
NHANES_Demo_1314 <- read_xpt("Data/DEMO_H.xpt")
```

```{r}
NHANES_BMI_1718 <- read_xpt("Data/BMX_J.xpt")
NHANES_BMI_1516 <- read_xpt("Data/BMX_I.xpt")
NHANES_BMI_1314 <- read_xpt("Data/BMX_H.xpt")
```

###DM(Diabetes Melliitus)

```{r}
NHANES_DM_1718 <- read_xpt("Data/DIQ_J.xpt")
NHANES_DM_1516 <- read_xpt("Data/DIQ_I.xpt")
NHANES_DM_1314 <- read_xpt("Data/DIQ_H.xpt")
```

## HINSUR

```{r}
NHANES_Hinsur_1718 <- read_xpt("Data/HIQ_J.xpt")
NHANES_Hinsur_1516 <- read_xpt("Data/HIQ_I.xpt")
NHANES_Hinsur_1314 <- read_xpt("Data/HIQ_H.xpt")
```

## (Medcon)

```{R}
NHANES_MC_1718 <- read_xpt("Data/MCQ_J.xpt")
NHANES_MC_1516 <- read_xpt("Data/MCQ_I.xpt")
NHANES_MC_1314 <- read_xpt("Data/MCQ_H.xpt")
```

## Physical Activty

```{r}
NHANES_PA_1718 <- read_xpt("Data/PAQ_J.xpt")
NHANES_PA_1516 <- read_xpt("Data/PAQ_I.xpt")
NHANES_PA_1314 <- read_xpt("Data/PAQ_H.xpt")
```

#Smoking

```{R}
NHANES_SMK_1718 <- read_xpt("Data/SMQ_J.xpt")
NHANES_SMK_1516 <- read_xpt("Data/SMQ_I.xpt")
NHANES_SMK_1314 <- read_xpt("Data/SMQ_H.xpt")
```

#Occupation

```{r}
NHANES_OC_1718 <- read_xpt("Data/OCQ_J.xpt")
NHANES_OC_1516 <- read_xpt("Data/OCQ_I.xpt")
NHANES_OC_1314 <- read_xpt("Data/OCQ_H.xpt")
```

```{R}
NHANES_demo_merged <- bind_rows(NHANES_Demo_1314, 
                         NHANES_Demo_1516, 
                         NHANES_Demo_1718)
```

```{r}
NHANES_BMI_merged <- bind_rows(NHANES_BMI_1314, 
                         NHANES_BMI_1516, 
                         NHANES_BMI_1718)
```

```{r}
NHANES_DM_merged <- bind_rows(NHANES_DM_1314, 
                         NHANES_DM_1516, 
                         NHANES_DM_1718)
```

```{r}
NHANES_Hinsur_merged <- bind_rows(NHANES_Hinsur_1314, 
                         NHANES_Hinsur_1516, 
                         NHANES_Hinsur_1718)
```

```{R}
NHANES_MC_merged <- bind_rows(NHANES_MC_1314, 
                         NHANES_MC_1516, 
                         NHANES_MC_1718)
```

```{r}
NHANES_PA_merged <- bind_rows(NHANES_PA_1314, 
                         NHANES_PA_1516, 
                         NHANES_PA_1718)
```

```{r}
NHANES_SMK_merged <- bind_rows(NHANES_SMK_1314, 
                         NHANES_SMK_1516, 
                         NHANES_SMK_1718)
```

```{r}
NHANES_OC_merged <- bind_rows(NHANES_OC_1314, 
                         NHANES_OC_1516, 
                         NHANES_OC_1718)
```

## Create analytic sample

```{R}
BMI_vars <- NHANES_BMI_merged %>% select( SEQN, BMXBMI)
SMK_vars <- NHANES_SMK_merged %>% select(SEQN, SMQ020, SMQ621)
DM_vars <- NHANES_DM_merged %>% select(SEQN, DIQ010)
Hinsur_vars <- NHANES_Hinsur_merged %>% select(SEQN , HIQ011)
MC_vars <- NHANES_MC_merged %>% select(SEQN, MCQ160A, MCQ195)
PA_vars <- NHANES_PA_merged %>% select(SEQN, PAQ605, PAQ610, PAQ620, PAD615, PAQ625, PAD630)
OC_vars <- NHANES_OC_merged %>% select(SEQN, OCD150)
```

#MET Score coding

```{r}
PA_vars <- PA_vars %>%
  mutate(
    vig_days = if_else(PAQ610 %in% c(77, 99), NA_real_, as.numeric(PAQ610)),
    vig_min  = if_else(PAD615 %in% c(7777, 9999), NA_real_, as.numeric(PAD615)),
    mod_days = if_else(PAQ625 %in% c(77, 99), NA_real_, as.numeric(PAQ625)),
    mod_min  = if_else(PAD630 %in% c(7777, 9999), NA_real_, as.numeric(PAD630)),
    MET_total = (vig_days * vig_min * 8) + (mod_days * mod_min * 4)
  )
```


```{r}
PA_vars <- PA_vars %>%
  mutate(
    MET_total = if_else(PAQ620 == 2 & is.na(MET_total),
                         vig_days * vig_min * 8, MET_total),
    MET_total = if_else(PAQ605 == 2 & is.na(MET_total),
                         mod_days * mod_min * 4, MET_total)
  )
```


```{r}
NHANES_analytic <- NHANES_demo_merged %>%
  left_join(BMI_vars,   by = "SEQN") %>%
  left_join(SMK_vars,   by = "SEQN") %>%
  left_join(DM_vars,    by = "SEQN") %>%
  left_join(Hinsur_vars, by = "SEQN") %>%
  left_join(MC_vars,    by = "SEQN") %>%
  left_join(PA_vars,    by = "SEQN") %>%
  left_join(OC_vars, by = "SEQN")

```

#BMI catagorical

Underweight/Normal = 0 Overweight = 1 Obese = 2

```{R}
NHANES_analytic <- NHANES_analytic %>%
  mutate(BMI_cat = case_when(
    BMXBMI < 25 ~ "Underweight/Normal",
    BMXBMI >= 25 & BMXBMI <= 30 ~ "Overweight",
    BMXBMI > 30 ~ "Obese",
    TRUE ~ NA_character_
  ))
```

#Mutate / Recode

Arthritis: MCQ 160a : 1 = Yes, 2= No , Other = 0

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    Arthritis = case_when(
      MCQ160A == 1 ~ 1,
      MCQ160A == 2 ~ 0,
      MCQ160A == 9 ~ 0,
      TRUE ~ NA_real_
    ),
    Osteoarthritis = case_when(
      MCQ195 == 1               ~ 1,
      MCQ195 %in% c(2, 3, 4)    ~ 0,
      MCQ195 %in% c(7, 9)       ~ NA_real_,
      TRUE                      ~ NA_real_
    ),
    Osteoarthritis = if_else(MCQ160A == 2, 0, Osteoarthritis),
    age_cat = case_when(
      RIDAGEYR >= 20 & RIDAGEYR <= 29 ~ "20-29",
      RIDAGEYR >= 30 & RIDAGEYR <= 44 ~ "30-44",
      RIDAGEYR >= 45 & RIDAGEYR <= 64 ~ "45-64",
      RIDAGEYR >= 65 ~ "65+"
    ),
    Hinsur_yn = case_when(
      HIQ011 == 1 ~ "Yes",
      HIQ011 == 2 ~ "No",
      TRUE ~ NA_character_
    ),
    smk_status = case_when(
      SMQ020 == 1 ~ "Yes",
      SMQ020 == 2 ~ "No"
    ),
     RE_cat = case_when(
       RIDRETH3 == 1 ~ "Mexican American",
       RIDRETH3 == 3 ~ "White",
       RIDRETH3 == 4 ~ "Black",
       RIDRETH3 == 6 ~ "Asian",
       RIDRETH3 == 2 |
       RIDRETH3 == 7 ~ "Mixed/Other"
     ),
    Sex_cat = case_when(
      RIAGENDR == 1 ~ "Male",
      RIAGENDR == 2 ~ "Female"
    ),
    Edu_yn = case_when(
      DMDEDUC2 == 5 ~ "College graduate and above",
      DMDEDUC2 == 1 ~ "Less than college education",
      DMDEDUC2 == 2 ~ "Less than college education",
      DMDEDUC2 == 3 ~ "Less than college education",
      DMDEDUC2 == 4 ~ "Less than college education",
      DMDEDUC2 == 7 ~ NA_character_,
      DMDEDUC2 == 9 ~ NA_character_,
      TRUE ~ NA_character_
    ),
    Income = case_when(
      INDFMPIR > 0 & INDFMPIR <= 1.3 ~ "<130% FPL",
      INDFMPIR > 1.3 & INDFMPIR <= 3.5 ~ "130-350% FPL",
      INDFMPIR > 3.5 ~ ">350% FPL"
    ),
    Diabetes = case_when(
      DIQ010 == 1 ~ "Yes",
      DIQ010 == 2 ~ "No",
      DIQ010 == 3 ~ "No",
      DIQ010 == 9 ~ "No",
      TRUE ~ NA_character_
    ),
    MET_tertile = ntile(MET_total, 3),  # splits into 3 equal groups
         MET_tertile = factor(MET_tertile,
                              levels = c(1, 2, 3),
                              labels = c("Low", "Medium", "High")),
    emp_st = case_when(
      OCD150 == 1 |
        OCD150 == 2 ~ "Currently working",
      OCD150 == 3 |
        OCD150 == 4 |
        OCD150 == 7 |
        OCD150 == 9 ~"Not currently working",
      TRUE ~ NA_character_
    ),
    newweight = WTMEC2YR / 3 
    )
```

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop1 = if_else(!is.na(WTMEC2YR) & WTMEC2YR > 0, 1, 0))

NHANES_analytic <- NHANES_analytic %>% 
   mutate(subpop2 = case_when(
    subpop1 == 1 &
    RIDAGEYR >= 20 & RIDAGEYR <= 64 &
    OCD150 %in% c(1, 2)    ~ 1,
    TRUE                    ~ 0
  ))

NHANES_analytic %>%
  filter(subpop2 == 1) %>%
  nrow()

NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop3 = if_else(subpop2 == 1 & !is.na(Osteoarthritis), 1, 0))
```

8950 with correct age and has arthritis

# Missing values

```{r}
NHANES_analytic<- NHANES_analytic %>%
  mutate(miss_dv = case_when(
    is.na(Osteoarthritis)  ~ 1,  
    .default = 0))



NHANES_analytic <- NHANES_analytic %>%
  mutate(miss_iv = case_when(
    is.na(MET_total) ~ 1,  
    .default= 0)) 

```

Counts of missing

```{r}
NHANES_analytic %>%
  filter(subpop1 == 1 & miss_dv == 0) %>%
  nrow()

NHANES_analytic %>%
  filter(subpop1 == 1 & miss_iv == 0) %>%
  nrow()
```

#subpop2

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop2 = case_when(
    subpop1 == 1 & miss_dv == 0 &
      miss_iv == 0 ~ 1,
    .default = 0
  ))

NHANES_analytic %>%
  filter(subpop2 == 1) %>%
  nrow()
```

#Svey Design

```{r}
des <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)
cuts <- svyquantile(~MET_total, des, quantiles = c(1/3, 2/3), na.rm = TRUE)
cut_lo <- as.numeric(cuts$MET_total[1, "quantile"])
cut_hi <- as.numeric(cuts$MET_total[2, "quantile"])

```


```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    met_cat = case_when(
      is.na(MET_total)                 ~ NA_real_,
      MET_total <= cut_lo               ~ 1,
      MET_total > cut_lo & MET_total <= cut_hi ~ 2,
      MET_total > cut_hi                ~ 3
    ),
    met_cat = if_else(PAQ605 == 2 & PAQ620 == 2, 0, met_cat)
  )
```

#Total: 29400 Participants of 64 variables

```{R}
# of cases age 
NHANES_analytic %>%
  filter(RIDAGEYR >= 20 & RIDAGEYR <= 65) %>%
  nrow()

```

20-65 yo : 13141

#Arthritis type


```{R}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop4 = if_else(subpop3 == 1 & !is.na(met_cat), 1, 0))

cat("subpop4 n =", sum(NHANES_analytic$subpop4 == 1), "\n")
```


```{R}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop5 = if_else(
    subpop4 == 1 &
      DMDEDUC2 <= 5 &
      RIDRETH1 <= 5 &
      RIAGENDR <= 2 &
      !is.na(RIDAGEYR) &
      !is.na(INDFMPIR) &
      !is.na(BMXBMI) &
      SMQ020 <= 2 &
      HIQ011 <= 2,
    1, 0
  ))

cat("subpop5 n =", sum(NHANES_analytic$subpop5 == 1), "\n")
```


```{r}
# Convert survey design variables to dataframe for tbl_summary
NHANES_analytic%>%
  filter(subpop5 == 1) %>%
  select(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile) %>%
  tbl_summary(
    by      = Osteoarthritis,
    missing = "no",
    label = list(
      MET_tertile    ~ "MET score by Tertiles",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 based on Osteoarthritis")
  #gtsave(filename = "Table1_byOA.docx")

```

### Table 1 by exposure

```{r}
# Convert survey design variables to dataframe for tbl_summary
NHANES_analytic %>%
  filter(subpop5 == 1) %>%
  select(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile) %>%
  tbl_summary(
    by      = MET_tertile,
    missing = "no",
    label = list(
      Osteoarthritis ~ "Has Osteoarthritis?",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 by MET level") 
 #  gtsave(filename = "Table1_OA_byMET.docx")
```
