---
title: "Data_cleaning"
format: html
self-contained : true
editor: visual
---

```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(readr)
library(rstatix)
library(janitor)
library(dplyr)
library(knitr)
library(haven)
library(gt)
library(gtsummary)
library(survey)
library(broom)
library(broom.helpers)
```

###Load data

```{r}
NHANES_Demo_1718 <- read_xpt("Data/DEMO_J.xpt")
NHANES_Demo_1516 <- read_xpt("Data/DEMO_I.xpt")
NHANES_Demo_1314 <- read_xpt("Data/DEMO_H.xpt")
```

```{r}
NHANES_BMI_1718 <- read_xpt("Data/BMX_J.xpt")
NHANES_BMI_1516 <- read_xpt("Data/BMX_I.xpt")
NHANES_BMI_1314 <- read_xpt("Data/BMX_H.xpt")
```

###DM(Diabetes Melliitus)

```{r}
NHANES_DM_1718 <- read_xpt("Data/DIQ_J.xpt")
NHANES_DM_1516 <- read_xpt("Data/DIQ_I.xpt")
NHANES_DM_1314 <- read_xpt("Data/DIQ_H.xpt")
```

## HINSUR

```{r}
NHANES_Hinsur_1718 <- read_xpt("Data/HIQ_J.xpt")
NHANES_Hinsur_1516 <- read_xpt("Data/HIQ_I.xpt")
NHANES_Hinsur_1314 <- read_xpt("Data/HIQ_H.xpt")
```

## (Medcon)

```{R}
NHANES_MC_1718 <- read_xpt("Data/MCQ_J.xpt")
NHANES_MC_1516 <- read_xpt("Data/MCQ_I.xpt")
NHANES_MC_1314 <- read_xpt("Data/MCQ_H.xpt")
```

## Physical Activty

```{r}
NHANES_PA_1718 <- read_xpt("Data/PAQ_J.xpt")
NHANES_PA_1516 <- read_xpt("Data/PAQ_I.xpt")
NHANES_PA_1314 <- read_xpt("Data/PAQ_H.xpt")
```

#Smoking

```{R}
NHANES_SMK_1718 <- read_xpt("Data/SMQ_J.xpt")
NHANES_SMK_1516 <- read_xpt("Data/SMQ_I.xpt")
NHANES_SMK_1314 <- read_xpt("Data/SMQ_H.xpt")
```

#Occupation

```{r}
NHANES_OC_1718 <- read_xpt("Data/OCQ_J.xpt")
NHANES_OC_1516 <- read_xpt("Data/OCQ_I.xpt")
NHANES_OC_1314 <- read_xpt("Data/OCQ_H.xpt")
```

```{R}
NHANES_demo_merged <- bind_rows(NHANES_Demo_1314, 
                         NHANES_Demo_1516, 
                         NHANES_Demo_1718)
```

```{r}
NHANES_BMI_merged <- bind_rows(NHANES_BMI_1314, 
                         NHANES_BMI_1516, 
                         NHANES_BMI_1718)
```

```{r}
NHANES_DM_merged <- bind_rows(NHANES_DM_1314, 
                         NHANES_DM_1516, 
                         NHANES_DM_1718)
```

```{r}
NHANES_Hinsur_merged <- bind_rows(NHANES_Hinsur_1314, 
                         NHANES_Hinsur_1516, 
                         NHANES_Hinsur_1718)
```

```{R}
NHANES_MC_merged <- bind_rows(NHANES_MC_1314, 
                         NHANES_MC_1516, 
                         NHANES_MC_1718)
```

```{r}
NHANES_PA_merged <- bind_rows(NHANES_PA_1314, 
                         NHANES_PA_1516, 
                         NHANES_PA_1718)
```

```{r}
NHANES_SMK_merged <- bind_rows(NHANES_SMK_1314, 
                         NHANES_SMK_1516, 
                         NHANES_SMK_1718)
```

```{r}
NHANES_OC_merged <- bind_rows(NHANES_OC_1314, 
                         NHANES_OC_1516, 
                         NHANES_OC_1718)
```

## Create analytic sample

```{R}
BMI_vars <- NHANES_BMI_merged %>% select( SEQN, BMXBMI)
SMK_vars <- NHANES_SMK_merged %>% select(SEQN, SMQ020, SMQ621)
DM_vars <- NHANES_DM_merged %>% select(SEQN, DIQ010)
Hinsur_vars <- NHANES_Hinsur_merged %>% select(SEQN , HIQ011)
MC_vars <- NHANES_MC_merged %>% select(SEQN, MCQ160A, MCQ195)
PA_vars <- NHANES_PA_merged %>% select(SEQN, PAQ605, PAQ610, PAQ620, PAD615, PAQ625, PAD630)
OC_vars <- NHANES_OC_merged %>% select(SEQN, OCD150)
```

#Create sample

```{r}
NHANES_analytic <- NHANES_demo_merged %>%
  left_join(BMI_vars,   by = "SEQN") %>%
  left_join(SMK_vars,   by = "SEQN") %>%
  left_join(DM_vars,    by = "SEQN") %>%
  left_join(Hinsur_vars, by = "SEQN") %>%
  left_join(MC_vars,    by = "SEQN") %>%
  left_join(PA_vars,    by = "SEQN") %>%
  left_join(OC_vars, by = "SEQN")

```

###Creating MET score

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    vig_days = case_when(
      PAQ605 == 2              ~ 0,          # No vigorous activity → 0 days
      PAQ610 %in% c(77, 99)   ~ 0,   # Refused/Don't know → NA
      PAQ605 == 1              ~ as.numeric(PAQ610),  # Valid response
      TRUE                     ~ NA_real_
    ),
    vig_min = case_when(
      PAQ605 == 2              ~ 0,          # No vigorous activity → 0 mins
      PAD615 %in% c(7777, 9999) ~ 0, # Refused/Don't know → NA
      PAQ605 == 1              ~ as.numeric(PAD615),  # Valid response
      TRUE                     ~ NA_real_
    ),
    # Step 3 — Moderate activity days
    # Only valid if PAQ620 == 1 (Yes to moderate activity)
    mod_days = case_when(
      PAQ620 == 2              ~ 0,          # No moderate activity → 0 days
      PAQ625 %in% c(77, 99)   ~ 0,   # Refused/Don't know → NA
      PAQ620 == 1              ~ as.numeric(PAQ625),  # Valid response
      TRUE                     ~ NA_real_
    ),
    # Step 4 — Moderate activity minutes
    # Only valid if PAQ620 == 1 (Yes to moderate activity)
    mod_min = case_when(
      PAQ620 == 2               ~ 0,         # No moderate activity → 0 mins
      PAD630 %in% c(7777, 9999) ~ 0,  # Refused/Don't know → NA
      PAQ620 == 1               ~ as.numeric(PAD630),  # Valid response
      TRUE                      ~ NA_real_
    ),
    MET_vig   = vig_days * vig_min * 8,    # vigorous MET
    MET_mod   = mod_days * mod_min * 4,    # moderate MET
    MET_total = case_when(
      is.na(MET_vig) & is.na(MET_mod) ~ 0,  # both missing → NA
      is.na(MET_vig)                  ~ MET_mod,    # only vig missing → use mod
      is.na(MET_mod)                  ~ MET_vig,    # only mod missing → use vig
      TRUE ~ MET_vig + MET_mod                      # both valid → sum
    )
  )
```

#BMI catagorical

Underweight/Normal = 0 Overweight = 1 Obese = 2

```{R}
NHANES_analytic <- NHANES_analytic %>%
  mutate(BMI_cat = case_when(
    BMXBMI < 25 ~ "Underweight/Normal",
    BMXBMI >= 25 & BMXBMI <= 30 ~ "Overweight",
    BMXBMI > 30 ~ "Obese",
    TRUE ~ NA_character_
  ))
```

#Mutate / Recode

Arthritis: MCQ 160a : 1 = Yes, 2= No , Other = 0

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    Arthritis = case_when(
      MCQ160A == 1 ~ 1,
      MCQ160A == 2 ~ 0,
      MCQ160A == 9 ~ 0,
      TRUE ~ NA_real_
    ),
    Osteoarthritis = case_when(
      MCQ160A == 2 ~ 0, # Skip patter no = 0
       MCQ160A == 1 & MCQ195 == 1               ~ 1,
      MCQ195 %in% c(2, 3, 4)    ~ 0,
      MCQ195 %in% c(7, 9)       ~ NA_real_,
      TRUE                      ~ NA_real_
    ),
    Osteoarthritis = if_else(MCQ160A == 2, 0, Osteoarthritis),
    age_cat = case_when(
      RIDAGEYR >= 20 & RIDAGEYR <= 29 ~ "20-29",
      RIDAGEYR >= 30 & RIDAGEYR <= 44 ~ "30-44",
      RIDAGEYR >= 45 & RIDAGEYR <= 64 ~ "45-64",
      RIDAGEYR >= 65 ~ "65+",
      TRUE ~ NA_character_
    ),
    Hinsur_yn = case_when(
      HIQ011 == 1 ~ "Yes",
      HIQ011 == 2 ~ "No",
      TRUE ~ NA_character_
    ),
    smk_status = case_when(
      SMQ020 == 1 ~ "Yes",
      SMQ020 == 2 ~ "No",
      TRUE ~ NA_character_
    ),
     RE_cat = case_when(
       RIDRETH3 == 1 ~ "Mexican American",
       RIDRETH3 == 3 ~ "White",
       RIDRETH3 == 4 ~ "Black",
       RIDRETH3 == 6 ~ "Asian",
       RIDRETH3 == 2 |
       RIDRETH3 == 7 ~ "Mixed/Other",
       TRUE ~ NA_character_
     ),
    Sex_cat = case_when(
      RIAGENDR == 1 ~ "Male",
      RIAGENDR == 2 ~ "Female",
      TRUE ~ NA_character_
    ),
    Edu_yn = case_when(
      DMDEDUC2 == 5 ~ "College graduate and above",
      DMDEDUC2 == 1 ~ "Less than college education",
      DMDEDUC2 == 2 ~ "Less than college education",
      DMDEDUC2 == 3 ~ "Less than college education",
      DMDEDUC2 == 4 ~ "Less than college education",
      DMDEDUC2 == 7 ~ NA_character_,
      DMDEDUC2 == 9 ~ NA_character_,
      TRUE ~ NA_character_
    ),
    Income = case_when(
      INDFMPIR > 0 & INDFMPIR <= 1.3 ~ "<130% FPL",
      INDFMPIR > 1.3 & INDFMPIR <= 3.5 ~ "130-350% FPL",
      INDFMPIR > 3.5 ~ ">350% FPL",
      TRUE ~ NA_character_
    ),
    Diabetes = case_when(
      DIQ010 == 1 ~ "Yes",
      DIQ010 == 2 ~ "No",
      DIQ010 == 3 ~ "No",
      DIQ010 == 9 ~ "No",
      TRUE ~ NA_character_
    ),
    MET_tertile = ntile(MET_total, 3),  # splits into 3 equal groups
         MET_tertile = factor(MET_tertile,
                              levels = c(1, 2, 3),
                              labels = c("Low", "Medium", "High")),
    emp_st = case_when(
      OCD150 == 1 |
        OCD150 == 2 ~ 1,
      OCD150 == 3 |
        OCD150 == 4 |
        OCD150 == 7 |
        OCD150 == 9 ~ 0,
      TRUE ~ NA_real_
    ),
    newweight = WTMEC2YR / 3 
    )
```

# Missing values

```{r}
NHANES_analytic<- NHANES_analytic %>%
  mutate(miss_dv = case_when(
    is.na(Osteoarthritis)  ~ 1,  
    .default = 0))



NHANES_analytic <- NHANES_analytic %>%
  mutate(miss_iv = case_when(
    is.na(MET_total) ~ 1,  
    .default= 0)) 

NHANES_analytic <- NHANES_analytic %>%
  mutate(miss_conf = case_when(
    is.na(age_cat)|
      is.na(Hinsur_yn)|
      is.na(smk_status)|
      is.na(RE_cat)|
      is.na(Sex_cat)|
      is.na(Edu_yn)|
      is.na(Income)|
      is.na(Diabetes)~ 1,  
    .default= 0)) 

```

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop1 = if_else(RIDSTATR == 2, 1, 0))

NHANES_analytic %>%
  filter(subpop1 == 1) %>%
  nrow()
```

```{r}
#Subpop for employed
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop2 = case_when(
    RIDSTATR == 2 &
      emp_st == 1 ~ 1,
    TRUE ~ 0
  ))

NHANES_analytic %>%
  filter(subpop2 == 1) %>%
  nrow()
```

#9812 w employment data and valid MEC (Subpop2)

#Create subpop for age

```{r}
NHANES_analytic <- NHANES_analytic %>% 
   mutate(subpop3 = case_when(
    RIDSTATR == 2 &
    RIDAGEYR >= 20 & RIDAGEYR <= 64 &
    emp_st == 1 ~ 1,
    TRUE                    ~ 0
  ))

NHANES_analytic %>%
  filter(subpop3 == 1) %>%
  nrow()
```

8523 with correct age and employed (Subpop3)

```{r}
##Making subpop 4 ( validated exposure MET)
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop4 = case_when(
    RIDSTATR == 2 &
    RIDAGEYR >= 20 & RIDAGEYR <= 64 &
    emp_st == 1 & miss_iv == 0 ~ 1,
    TRUE                    ~ 0
  ))

NHANES_analytic %>%
  filter(subpop4 == 1) %>%
  nrow()
```

8523 with correct age and employed with valid PA data (Subpop4)

#subpop5 (Valid outcome)

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop5 = case_when(
    RIDSTATR == 2 &
    RIDAGEYR >= 20 & RIDAGEYR <= 64 &
    emp_st == 1 & miss_iv == 0 &
      miss_dv == 0~ 1,
    TRUE                    ~ 0
  ))
NHANES_analytic %>%
  filter(subpop5 == 1) %>%
  nrow()
```

#8200 participants with valid inclusion and no omissing IV or DV

#Making subpop 6 (Missing covariates)

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop6 = case_when(
    RIDSTATR == 2 &
    RIDAGEYR >= 20 & RIDAGEYR <= 64 &
    emp_st == 1 & miss_iv == 0 &
      miss_dv == 0 & miss_conf == 0 ~ 1,
    TRUE                    ~ 0))

NHANES_analytic %>%
  filter(subpop6 == 1) %>%
  nrow()
```

#7411 with completed data =\> final analytical sample

#Svey Design

```{r}
des <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)
cuts <- svyquantile(~MET_total, des, quantiles = c(1/3, 2/3), na.rm = TRUE)
cut_lo <- as.numeric(cuts$MET_total[1, "quantile"])
cut_hi <- as.numeric(cuts$MET_total[2, "quantile"])

```

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    met_cat = case_when(
      is.na(MET_total)                 ~ NA_real_,
      MET_total == 0 ~ 0,
      MET_total <= cut_lo               ~ 1,
      MET_total > cut_lo & MET_total <= cut_hi ~ 2,
      MET_total > cut_hi                ~ 3
    ),
    met_cat = if_else(PAQ605 == 2 & PAQ620 == 2, 0, met_cat)
  )
```

##Making svey design?

```{r}
OAsvyset <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)

analytic_subpop <- subset(OAsvyset, subpop6 == 1)
```

```{r}
# Convert survey design variables to dataframe for tbl_summary
tbl_svysummary( data = analytic_subpop,
    by      = Osteoarthritis,
    include = c(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile),
    statistic = list(
      all_continuous()  ~ "{mean} ({mean.std.error})",  # weighted mean and SE
      all_categorical() ~ "{n_unweighted} ({p}%)"       # unweighted n, weighted %
    ),
      digits = list(
      all_continuous()  ~ 1,
      all_categorical() ~ c(0, 1)
    ),
    label = list(
      MET_tertile    ~ "MET score by Tertiles",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    ),
    missing = "no"
  ) %>%
  add_overall() %>%
  modify_header(
    stat_0 ~ "**Overall**  \nN = {n_unweighted}",
    stat_1 ~ "**No Arthritis**  \nN = {n_unweighted}", 
    stat_2 ~ "**Arthrittis**  \nN = {n_unweighted}"# 👈 unweighted N in header
  ) %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 based on Osteoarthritis")
  #gtsave(filename = "Table1_byOA1.docx")

```

### Table 1 by exposure

```{r}
# Convert survey design variables to dataframe for tbl_summary
tbl_svysummary( data = analytic_subpop,
    by      = MET_tertile,
    include = c(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile),
    statistic = list(
      all_continuous()  ~ "{mean} ({mean.std.error})",  # weighted mean and SE
      all_categorical() ~ "{n_unweighted} ({p}%)"       # unweighted n, weighted %
    ),
      digits = list(
      all_continuous()  ~ 1,
      all_categorical() ~ c(0, 1)
    ),
    label = list(
      Osteoarthritis    ~ "Has Osteoarthritis",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    ),
    missing = "no"
  ) %>%
  add_overall() %>%
  modify_header(
    stat_0 ~ "**Overall**  \nN = {n_unweighted}",
    stat_1 ~ "**Low MET**  \nN = {n_unweighted}", 
    stat_2 ~ "**Moderate MET**  \nN = {n_unweighted}",
    stat_3 ~ "**High MET**  \nN = {n_unweighted}"# 👈 unweighted N in header
  ) %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 by MET level")
#gtsave(filename = "Table1_OA_byME1T.docx")
```

###Creating table2 (Sara)

```{r}
des <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)
analytic_design <- subset(des, subpop6 == 1)

unweighted_n <- NHANES_analytic %>%
filter(subpop6 == 1) %>%
count(MET_tertile)

weighted_pct <- as.data.frame(prop.table(svytable(~MET_tertile, analytic_design)) * 100)

descriptive <- unweighted_n %>%
left_join(weighted_pct, by = "MET_tertile") %>%
mutate(N_pct = paste0(n, " (", round(Freq, 1), "%)")) %>% select(MET_tertile, N_pct)


oa_prev <- svyby(~Osteoarthritis, ~MET_tertile, analytic_design,svyciprop, vartype = "ci", method = "logit")

oa_prev <- oa_prev %>%
mutate(Prev_CI = paste0(round(Osteoarthritis * 100, 1), "% (",
                          round(ci_l * 100, 1), "-", round(ci_u * 100, 1), "%)")) %>%
select(MET_tertile, Prev_CI)


crude_model <- svyglm(Osteoarthritis ~ MET_tertile,design = analytic_design, family = quasibinomial())

crude_ci <- exp(cbind(OR = coef(crude_model), confint(crude_model)))

crude_df <- data.frame(MET_tertile = c("Low", "Medium", "High"),Crude_OR = c("1.00 (Reference)",paste0(round(crude_ci[2,1], 2), " (", round(crude_ci[2,2], 2), "-", round(crude_ci[2,3], 2), ")"), paste0(round(crude_ci[3,1], 2), " (", round(crude_ci[3,2], 2), "-", round(crude_ci[3,3], 2), ")")))


adj_model <- svyglm(Osteoarthritis ~ MET_tertile + RIDAGEYR + Sex_cat + RE_cat + BMXBMI + smk_status + Diabetes + INDFMPIR,design = analytic_design, family = quasibinomial())

adj_ci <- exp(cbind(OR = coef(adj_model), confint(adj_model)))

adj_df <- data.frame(
  MET_tertile = c("Low", "Medium", "High"),
  Adjusted_OR = c("1.00 (Reference)",
                  paste0(round(adj_ci[2,1], 2), " (", round(adj_ci[2,2], 2), "-", round(adj_ci[2,3], 2), ")"),
                  paste0(round(adj_ci[3,1], 2), " (", round(adj_ci[3,2], 2), "-", round(adj_ci[3,3], 2), ")"))
)

table2 <- descriptive %>%
  left_join(oa_prev, by = "MET_tertile") %>%
  left_join(crude_df, by = "MET_tertile") %>%
  left_join(adj_df, by = "MET_tertile") %>%
  rename(
    "MET Tertile" = MET_tertile,
    "N (Weighted %)" = N_pct,
    "Osteoarthritis Prevalence (95% CI)" = Prev_CI,
    "Crude OR (95% CI)" = Crude_OR,
    "Adjusted OR (95% CI)" = Adjusted_OR
  )
footnote_text <- paste0(
  "MET tertiles based on survey-weighted cutpoints: Low ≤", round(cut_lo, 0),
  ", Medium ", round(cut_lo, 0), "-", round(cut_hi, 0),
  ", High >", round(cut_hi, 0),
  ". Adjusted model controls for age, sex, race/ethnicity, BMI, smoking status, diabetes, and income-to-poverty ratio."
)

table2 %>%
gt() %>%
tab_header(
  title = "Table 2: Association Between Occupational Physical Activity and Osteoarthritis",
    subtitle = "NHANES 2013-2018, Employed U.S. Adults Aged 20-64"
  ) %>%
  tab_footnote(footnote = footnote_text)
```

##Creating table 3

# Make stratified models
```{r}
# Stratum 1 — Health Insurance
model_male <- svyglm(
  Osteoarthritis ~ MET_tertile + age_cat + RE_cat + 
                   BMI_cat + smk_status + Sex_cat + 
                   Income + Edu_yn + Diabetes,
  design = subset(analytic_subpop, Hinsur_yn == "Yes"),
  family = quasibinomial()
)

# Stratum 2 — No Health Insurance
model_female <- svyglm(
  Osteoarthritis ~ MET_tertile + age_cat + RE_cat + 
                   BMI_cat + smk_status + Sex_cat + 
                   Income + Edu_yn + Diabetes,
  design = subset(analytic_subpop, Hinsur_yn == "No"),
  family = quasibinomial()
)

#Stratum 3 -> Has higher education
model_male <- svyglm(
  Osteoarthritis ~ MET_tertile + age_cat + RE_cat + 
                   BMI_cat + smk_status + Sex_cat + 
                   Income + Diabetes + Hinsur_yn,
  design = subset(analytic_subpop, Edu_yn == "College graduate and above"),
  family = quasibinomial()
)

# Stratum 4 — No Higher Education
model_female <- svyglm(
  Osteoarthritis ~ MET_tertile + age_cat + RE_cat + 
                   BMI_cat + smk_status + Sex_cat + 
                   Income + Hinsur_yn + Diabetes,
  design = subset(analytic_subpop, Edu_yn == "Less than college education"),
  family = quasibinomial()
)
```

###Obtain counts and proprtions
```{r}
# Counts and weighted % for each stratum
get_counts <- function(des, stratum_var, stratum_val) {
  sub <- subset(des, get(stratum_var) == stratum_val)
  
  # Total N per MET tertile
  tot <- svyby(~Osteoarthritis, ~MET_tertile, sub, 
               svytotal, na.rm = TRUE)
  
  # Weighted % per MET tertile
  pct <- svyby(~Osteoarthritis, ~MET_tertile, sub,
               svymean, na.rm = TRUE)
  
  list(total = tot, pct = pct)
}

counts_male   <- get_counts(subpop_design, "Sex_cat", "Male")
counts_female <- get_counts(subpop_design, "Sex_cat", "Female")
```
