---
title: "Data cleaning"
format: html
editor: visual
---

```{r}
library(here)
library(tidyverse)
library(ggplot2)
library(readr)
library(rstatix)
library(janitor)
library(dplyr)
library(knitr)
library(haven)
library(gt)
library(gtsummary)
library(survey)
```

### Load data

```{r}
NHANES_Demo_1718 <- read_xpt("DEMO_J.xpt")
NHANES_Demo_1516 <- read_xpt("DEMO_I.xpt")
NHANES_Demo_1314 <- read_xpt("DEMO_H.xpt")
```

```{r}
NHANES_BMI_1718 <- read_xpt("BMX_J.xpt")
NHANES_BMI_1516 <- read_xpt("BMX_I.xpt")
NHANES_BMI_1314 <- read_xpt("BMX_H.xpt")
```

### DM (Diabetes Mellitus)

```{r}
NHANES_DM_1718 <- read_xpt("DIQ_J.xpt")
NHANES_DM_1516 <- read_xpt("DIQ_I.xpt")
NHANES_DM_1314 <- read_xpt("DIQ_H.xpt")
```

## HINSUR

```{r}
NHANES_Hinsur_1718 <- read_xpt("HIQ_J.xpt")
NHANES_Hinsur_1516 <- read_xpt("HIQ_I.xpt")
NHANES_Hinsur_1314 <- read_xpt("HIQ_H.xpt")
```

## (Medcon)

```{r}
NHANES_MC_1718 <- read_xpt("MCQ_J.xpt")
NHANES_MC_1516 <- read_xpt("MCQ_I.xpt")
NHANES_MC_1314 <- read_xpt("MCQ_H.xpt")
```

## Physical Activity

```{r}
NHANES_PA_1718 <- read_xpt("PAQ_J.xpt")
NHANES_PA_1516 <- read_xpt("PAQ_I.xpt")
NHANES_PA_1314 <- read_xpt("PAQ_H.xpt")
```

# Smoking

```{r}
NHANES_SMK_1718 <- read_xpt("SMQ_J.xpt")
NHANES_SMK_1516 <- read_xpt("SMQ_I.xpt")
NHANES_SMK_1314 <- read_xpt("SMQ_H.xpt")
```

# Occupation

```{r}
NHANES_OC_1718 <- read_xpt("OCQ_J.xpt")
NHANES_OC_1516 <- read_xpt("OCQ_I.xpt")
NHANES_OC_1314 <- read_xpt("OCQ_H.xpt")
```

```{r}
NHANES_demo_merged <- bind_rows(NHANES_Demo_1314,NHANES_Demo_1516,NHANES_Demo_1718)
```

```{r}
NHANES_BMI_merged <- bind_rows(NHANES_BMI_1314, NHANES_BMI_1516, NHANES_BMI_1718)
```

```{r}
NHANES_DM_merged <- bind_rows(NHANES_DM_1314,
NHANES_DM_1516,NHANES_DM_1718)
```

```{r}
NHANES_Hinsur_merged <- bind_rows(NHANES_Hinsur_1314, NHANES_Hinsur_1516, NHANES_Hinsur_1718)
```

```{r}
NHANES_MC_merged <- bind_rows(NHANES_MC_1314, NHANES_MC_1516,NHANES_MC_1718)
```

```{r}
NHANES_PA_merged <- bind_rows(NHANES_PA_1314,
NHANES_PA_1516, NHANES_PA_1718)
```

```{r}
NHANES_SMK_merged <- bind_rows(NHANES_SMK_1314,
NHANES_SMK_1516, NHANES_SMK_1718)
```

```{r}
NHANES_OC_merged <- bind_rows(NHANES_OC_1314,
NHANES_OC_1516,NHANES_OC_1718)
```

## Create analytic sample

```{r}
BMI_vars <- NHANES_BMI_merged %>% select(SEQN, BMXBMI)
SMK_vars <- NHANES_SMK_merged %>% select(SEQN, SMQ020, SMQ621)
DM_vars <- NHANES_DM_merged %>% select(SEQN, DIQ010)
Hinsur_vars <- NHANES_Hinsur_merged %>% select(SEQN, HIQ011)
MC_vars <- NHANES_MC_merged %>% select(SEQN, MCQ160A, MCQ195)
PA_vars <- NHANES_PA_merged %>% select(SEQN, PAQ605, PAQ610, PAQ620, PAD615, PAQ625, PAD630)
OC_vars <- NHANES_OC_merged %>% select(SEQN, OCD150)
```

# MET Score coding

```{r}
PA_vars <- PA_vars %>%
mutate(
vig_days = if_else(PAQ610 %in% c(77, 99), NA_real_, as.numeric(PAQ610)),
vig_min  = if_else(PAD615 %in% c(7777, 9999), NA_real_, as.numeric(PAD615)),
mod_days = if_else(PAQ625 %in% c(77, 99), NA_real_, as.numeric(PAQ625)),
mod_min  = if_else(PAD630 %in% c(7777, 9999), NA_real_, as.numeric(PAD630)),
MET_total = (vig_days * vig_min * 8) + (mod_days * mod_min * 4))
```

```{r}
PA_vars <- PA_vars %>%
mutate(MET_total = if_else(PAQ620 == 2 & is.na(MET_total),vig_days * vig_min * 8, MET_total),
MET_total = if_else(PAQ605 == 2 & is.na(MET_total), mod_days * mod_min * 4, MET_total))
```

```{r}
NHANES_analytic <- NHANES_demo_merged %>%
left_join(BMI_vars,   by = "SEQN") %>%
left_join(SMK_vars,   by = "SEQN") %>%
left_join(DM_vars,    by = "SEQN") %>%
left_join(Hinsur_vars, by = "SEQN") %>%
left_join(MC_vars,    by = "SEQN") %>%
left_join(PA_vars,    by = "SEQN") %>%
left_join(OC_vars, by = "SEQN")
```

# BMI categorical

Underweight/Normal = 0, Overweight = 1, Obese = 2

```{r}
NHANES_analytic <- NHANES_analytic %>%
mutate(BMI_cat = case_when(
BMXBMI < 25 ~ "Underweight/Normal",
BMXBMI >= 25 & BMXBMI <= 30 ~ "Overweight",
BMXBMI > 30 ~ "Obese",
TRUE ~ NA_character_ ))
```

# Mutate / Recode

Arthritis: MCQ160A: 1 = Yes, 2 = No, Other = 0

```{r}
NHANES_analytic <- NHANES_analytic %>%
mutate(Arthritis = case_when(
MCQ160A == 1 ~ 1,
MCQ160A == 2 ~ 0,
MCQ160A == 9 ~ 0,TRUE ~ NA_real_),Osteoarthritis = case_when(MCQ195 == 1~ 1, MCQ195 %in% c(2, 3, 4)    ~ 0, MCQ195 %in% c(7, 9)       ~ NA_real_,
 TRUE                      ~ NA_real_),
Osteoarthritis = if_else(MCQ160A == 2, 0, Osteoarthritis),
    age_cat = case_when(
      RIDAGEYR >= 20 & RIDAGEYR <= 29 ~ "20-29",
      RIDAGEYR >= 30 & RIDAGEYR <= 44 ~ "30-44",
      RIDAGEYR >= 45 & RIDAGEYR <= 64 ~ "45-64",
      RIDAGEYR >= 65 ~ "65+"
    ),
    Hinsur_yn = case_when(
      HIQ011 == 1 ~ "Yes",
      HIQ011 == 2 ~ "No",
      TRUE ~ NA_character_
    ),
    smk_status = case_when(
      SMQ020 == 1 ~ "Yes",
      SMQ020 == 2 ~ "No"
    ),
    RE_cat = case_when(
      RIDRETH3 == 1 ~ "Mexican American",
      RIDRETH3 == 3 ~ "White",
      RIDRETH3 == 4 ~ "Black",
      RIDRETH3 == 6 ~ "Asian",
      RIDRETH3 == 2 |
      RIDRETH3 == 7 ~ "Mixed/Other"
    ),
    Sex_cat = case_when(
      RIAGENDR == 1 ~ "Male",
      RIAGENDR == 2 ~ "Female"
    ),
    Edu_yn = case_when(
      DMDEDUC2 == 5 ~ "College graduate and above",
      DMDEDUC2 == 1 ~ "Less than college education",
      DMDEDUC2 == 2 ~ "Less than college education",
      DMDEDUC2 == 3 ~ "Less than college education",
      DMDEDUC2 == 4 ~ "Less than college education",
      DMDEDUC2 == 7 ~ NA_character_,
      DMDEDUC2 == 9 ~ NA_character_,
      TRUE ~ NA_character_
    ),
    Income = case_when(
      INDFMPIR > 0 & INDFMPIR <= 1.3 ~ "<130% FPL",
      INDFMPIR > 1.3 & INDFMPIR <= 3.5 ~ "130-350% FPL",
      INDFMPIR > 3.5 ~ ">350% FPL"
    ),
    Diabetes = case_when(
      DIQ010 == 1 ~ "Yes",
      DIQ010 == 2 ~ "No",
      DIQ010 == 3 ~ "No",
      DIQ010 == 9 ~ "No",
      TRUE ~ NA_character_
    ),
    MET_tertile = ntile(MET_total, 3),
    MET_tertile = factor(MET_tertile,
                         levels = c(1, 2, 3),
                         labels = c("Low", "Medium", "High")),
    emp_st = case_when(
      OCD150 == 1 |
        OCD150 == 2 ~ "Currently working",
      OCD150 == 3 |
        OCD150 == 4 |
        OCD150 == 7 |
        OCD150 == 9 ~ "Not currently working",
      TRUE ~ NA_character_
    ),
    newweight = WTMEC2YR / 3
  )
```

```{r}
NHANES_analytic <- NHANES_analytic %>%
mutate(subpop1 = if_else(!is.na(WTMEC2YR) & WTMEC2YR > 0, 1, 0))

NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop2 = case_when(
    subpop1 == 1 &
    RIDAGEYR >= 20 & RIDAGEYR <= 64 &
    OCD150 %in% c(1, 2)    ~ 1,
    TRUE                    ~ 0
  ))

NHANES_analytic %>%
  filter(subpop2 == 1) %>%
  nrow()

NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop3 = if_else(subpop2 == 1 & !is.na(Osteoarthritis), 1, 0))
```

8950 with correct age and has arthritis

# Missing values

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(miss_dv = case_when(
    is.na(Osteoarthritis)  ~ 1,
    .default = 0))

NHANES_analytic <- NHANES_analytic %>%
  mutate(miss_iv = case_when(
    is.na(MET_total) ~ 1,
    .default = 0))
```

Counts of missing

```{r}
NHANES_analytic %>%
  filter(subpop1 == 1 & miss_dv == 0) %>%
  nrow()

NHANES_analytic %>%
  filter(subpop1 == 1 & miss_iv == 0) %>%
  nrow()
```

# subpop2

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop2 = case_when(
    subpop1 == 1 & miss_dv == 0 &
      miss_iv == 0 ~ 1,
    .default = 0))

NHANES_analytic %>%
  filter(subpop2 == 1) %>%
  nrow()
```

# Survey Design

```{r}
des <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)
cuts <- svyquantile(~MET_total, des, quantiles = c(1/3, 2/3), na.rm = TRUE)
cut_lo <- as.numeric(cuts$MET_total[1, "quantile"])
cut_hi <- as.numeric(cuts$MET_total[2, "quantile"])
```

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(
    met_cat = case_when(
      is.na(MET_total)                 ~ NA_real_,
      MET_total <= cut_lo               ~ 1,
      MET_total > cut_lo & MET_total <= cut_hi ~ 2,
      MET_total > cut_hi                ~ 3
    ),
    met_cat = if_else(PAQ605 == 2 & PAQ620 == 2, 0, met_cat)
  )
```

# Total: 29400 Participants of 64 variables

```{r}
NHANES_analytic %>%
  filter(RIDAGEYR >= 20 & RIDAGEYR <= 65) %>%
  nrow()
```

20-65 yo: 13141

# Arthritis type

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop4 = if_else(subpop3 == 1 & !is.na(met_cat), 1, 0))

cat("subpop4 n =", sum(NHANES_analytic$subpop4 == 1), "\n")
```

```{r}
NHANES_analytic <- NHANES_analytic %>%
  mutate(subpop5 = if_else(
    subpop4 == 1 &
      DMDEDUC2 <= 5 &
      RIDRETH1 <= 5 &
      RIAGENDR <= 2 &
      !is.na(RIDAGEYR) &
      !is.na(INDFMPIR) &
      !is.na(BMXBMI) &
      SMQ020 <= 2 &
      HIQ011 <= 2,
    1, 0
  ))

cat("subpop5 n =", sum(NHANES_analytic$subpop5 == 1), "\n")
```

```{r}
NHANES_analytic %>%
  filter(subpop5 == 1) %>%
  select(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile) %>%
  tbl_summary(
    by      = Osteoarthritis,
    missing = "no",
    label = list(
      MET_tertile ~ "MET score by Tertiles",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 based on Osteoarthritis")
```

### Table 1 by exposure

```{r}
NHANES_analytic %>%
  filter(subpop5 == 1) %>%
  select(MET_total, Hinsur_yn,
         RE_cat, BMI_cat, age_cat, smk_status,
         Sex_cat, Income, Edu_yn, Diabetes,
         Osteoarthritis, MET_tertile) %>%
  tbl_summary(
    by      = MET_tertile,
    missing = "no",
    label = list(
      Osteoarthritis ~ "Has Osteoarthritis?",
      MET_total  ~ "Total MET score",
      Hinsur_yn  ~ "Health Insurance",
      RE_cat     ~ "Race and Ethnicity",
      BMI_cat    ~ "BMI",
      age_cat    ~ "Age",
      smk_status ~ "Smoking Status",
      Sex_cat    ~ "Sex",
      Income     ~ "Income",
      Edu_yn     ~ "Higher Education",
      Diabetes   ~ "Diabetes"
    )
  ) %>%
  add_overall() %>%
  bold_labels() %>%
  as_gt() %>%
  tab_header("Descriptive Characteristics for Analytic Sample between 20-64 by MET level")
```

# 

```{r}

des <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)
analytic_design <- subset(des, subpop5 == 1)
crude_model <- svyglm(Osteoarthritis ~ MET_tertile,design = analytic_design,family = quasibinomial())
adj_model <- svyglm(Osteoarthritis ~ MET_tertile + RIDAGEYR + Sex_cat + RE_cat + BMXBMI + smk_status + Diabetes + INDFMPIR,design = analytic_design,family = quasibinomial())

tbl_crude <- tbl_regression(crude_model, exponentiate = TRUE,
label = list(MET_tertile ~ "MET Tertile"))

tbl_adj <- tbl_regression(adj_model, exponentiate = TRUE,include = MET_tertile,label = list(MET_tertile ~ "MET Tertile"))

tbl_merge(list(tbl_crude, tbl_adj),
tab_spanner = c("**Crude OR (95% CI)**", "**Adjusted OR (95% CI)**")) %>%
as_gt() %>%
tab_header("Table 2: Association Between Occupational Physical Activity and Osteoarthritis") 

```

Table 2 (correct one)

```{r}

des <- svydesign(ids = ~1, weights = ~newweight, data = NHANES_analytic)
analytic_design <- subset(des, subpop5 == 1)

unweighted_n <- NHANES_analytic %>%
filter(subpop5 == 1) %>%
count(MET_tertile)

weighted_pct <- as.data.frame(prop.table(svytable(~MET_tertile, analytic_design)) * 100)

descriptive <- unweighted_n %>%
left_join(weighted_pct, by = "MET_tertile") %>%
mutate(N_pct = paste0(n, " (", round(Freq, 1), "%)")) %>% select(MET_tertile, N_pct)


oa_prev <- svyby(~Osteoarthritis, ~MET_tertile, analytic_design,svyciprop, vartype = "ci", method = "logit")

oa_prev <- oa_prev %>%
mutate(Prev_CI = paste0(round(Osteoarthritis * 100, 1), "% (",
                          round(ci_l * 100, 1), "-", round(ci_u * 100, 1), "%)")) %>%
select(MET_tertile, Prev_CI)


crude_model <- svyglm(Osteoarthritis ~ MET_tertile,design = analytic_design, family = quasibinomial())

crude_ci <- exp(cbind(OR = coef(crude_model), confint(crude_model)))

crude_df <- data.frame(MET_tertile = c("Low", "Medium", "High"),Crude_OR = c("1.00 (Reference)",paste0(round(crude_ci[2,1], 2), " (", round(crude_ci[2,2], 2), "-", round(crude_ci[2,3], 2), ")"), paste0(round(crude_ci[3,1], 2), " (", round(crude_ci[3,2], 2), "-", round(crude_ci[3,3], 2), ")")))


adj_model <- svyglm(Osteoarthritis ~ MET_tertile + RIDAGEYR + Sex_cat + RE_cat + BMXBMI + smk_status + Diabetes + INDFMPIR,design = analytic_design, family = quasibinomial())

adj_ci <- exp(cbind(OR = coef(adj_model), confint(adj_model)))

adj_df <- data.frame(
  MET_tertile = c("Low", "Medium", "High"),
  Adjusted_OR = c("1.00 (Reference)",
                  paste0(round(adj_ci[2,1], 2), " (", round(adj_ci[2,2], 2), "-", round(adj_ci[2,3], 2), ")"),
                  paste0(round(adj_ci[3,1], 2), " (", round(adj_ci[3,2], 2), "-", round(adj_ci[3,3], 2), ")"))
)

table2 <- descriptive %>%
  left_join(oa_prev, by = "MET_tertile") %>%
  left_join(crude_df, by = "MET_tertile") %>%
  left_join(adj_df, by = "MET_tertile") %>%
  rename(
    "MET Tertile" = MET_tertile,
    "N (Weighted %)" = N_pct,
    "Osteoarthritis Prevalence (95% CI)" = Prev_CI,
    "Crude OR (95% CI)" = Crude_OR,
    "Adjusted OR (95% CI)" = Adjusted_OR
  )
footnote_text <- paste0(
  "MET tertiles based on survey-weighted cutpoints: Low ≤", round(cut_lo, 0),
  ", Medium ", round(cut_lo, 0), "-", round(cut_hi, 0),
  ", High >", round(cut_hi, 0),
  ". Adjusted model controls for age, sex, race/ethnicity, BMI, smoking status, diabetes, and income-to-poverty ratio."
)

table2 %>%
gt() %>%
tab_header(
  title = "Table 2: Association Between Occupational Physical Activity and Osteoarthritis",
    subtitle = "NHANES 2013-2018, Employed U.S. Adults Aged 20-64"
  ) %>%
  tab_footnote(footnote = footnote_text)

```
